title

### 2016-05-13 paper.tex
paper: updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

This trend is not limited to Ceph. AWS Lambda, Redis Lua, Redis Modules,
KV-Drives, and Rhea, are all recent examples of storage systems embracing the
power of including application-specific semantics. While Ceph has not yet
reached the point of directly exposing these features to users, the recent
inclusion of a mechanism for dynamically defining extensions using
Lua~\cite{cls_lua} suggests that aspects of this may soon appear.

If the growth illustrated in Figure~\ref{fig:objclass-dev} continues, the
amount of low-level C++ is likely to grow very larage. Unfortunately, much of
this code is written assuming a performance profile defined by a combination
of the hardware and software versions available at the time of development. As
Ceph development continues at a fast pace, the cost of adapting to changing
assumptions regarding performance will become significant.

@@

In order to avoid this we need declarative magic hats.

@@

@@

@@

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{2}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & BS  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & WR  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{t:init-ds}
\end{table}

>>>>

This trend is also not limited to Ceph. AWS Lambda, Redis Lua, Redis Modules,
KV-Drives, and Rhea, are all recent examples of storage systems embracing the
power of including application-specific semantics. While Ceph has not yet
reached the point of directly exposing these features to users, the recent
inclusion of a mechanism for dynamically defining extensions using
Lua~\cite{cls_lua} suggests that aspects of this may soon appear.

If the growth illustrated in Figure~\ref{fig:objclass-dev} continues, the
amount of low-level C++ will grow large. Unfortunately, much of
this code is written assuming a performance profile defined by a combination
of the hardware and software versions available at the time of development. As
Ceph development continues at a fast pace, the cost of adapting to changing
assumptions regarding performance will become significant.

@@

Previous work in active storage has focused on the utility of moving
computation closer to data in an effort to reduce data movement and take
advantage of cpu and i/o parallelism, and gave little to no attention to
security or performance isolation concerns. In contrast, the interfaces being
deployed today focus on data management, indexing, and physical format.

We propose the introduction of a declarative language for building object
based interfaces that allows a storage system to meet the needs of an
application throughout the development process without requiring rewrites.

@@

Lets motivate here. Showing the need for programmability and some 
declarative interface.

Describe corfu and object class interfaces.

@@

Use state diagram to show how this works for corfu.

then show physical design crazy ness as we go to different
versions and/or different hardware.

\section{Programming Model}

Here we create a programming model for the objects

Show how the corfu interface is defined in this model.

\section{Other Interfaces}

\section{Evaluation}

@@

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & BS  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & WR  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{t:init-ds}
\end{table}
